\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks=true]{hyperref}
\title{PGP Frequently Asked Questions with Answers}
\author{Jeff Licquia\\\href{mailto:jalicqui@prairienet.org}{jalicqui@prairienet.org}}
\date{22 June 1995}
\begin{document}

\maketitle

\begin{abstract}
The use of PGP raises a number of political and issues. I am not a lawyer and am not qualified to give any legal opinions. Nothing in this document should be interpreted as legal advice. If you have any legal questions concerning the use of PGP, you should consult an attorney who specialises in patent and/or export law. In any case, the law will vary from country to country.
\end{abstract}

\tableofcontents

\section{Introduction}
This is the list of Frequently Asked Questions for the Pretty Good Privacy (PGP) encryption program written by Phillip Zimmermann. It is one of two FAQ lists for the newsgroup alt.security.pgp.

The other FAQ list is the "Where to Get PGP" FAQ, which is written and maintained by Michael Paul Johnson <mpj@netcom.com>. It covers many topics this one does not; in particular, it contains more complete information on sites that distribute PGP and the legal and technical questions surrounding its distribution. You may get a current copy from: \url{ftp://ftp.csn.net/mpj/getpgp.asc}

This FAQ is slanted towards the DOS or Unix users of PGP and many of the examples given may only apply to them. For other systems, I would like to direct your attention to the following documents:
\begin{itemize}
\item MAC: ``Here's How to MacPGP!'' by Xenon \href{mailto:an48138@anon.penet.fi}{an48138@anon.penet.fi}.
\item Archimedes PGP comes with its own PGPhints file.
\item Send e-mail to pgpinfo@mantis.co.uk for a list of PGP tips
\end{itemize}

It should be noted that most of the questions and answers concerning PGP apply equally well to the ViaCrypt(tm) version.

Material for this FAQ has come from many different sources. It would be difficult to name each of the contributors individually, but I would like to thank them as a group for their assistance.

A current copy of this FAQ can be retrieved from my WWW home page: \url{http://www.prairienet.org/~jalicqui/pgpfaq.txt} or via FTP: \url{ftp://ftp.prairienet.org/pub/providers/pgp/}

The ? indicates the file format: clearsigned text (txt), gzipped version of clearsigned text (txt.gz), PGP-signed-and-compressed binary (pgp), or ASCII armored PGP-signed-and-compressed file (asc).

The PGP FAQ is also posted to news.answers and alt.answers, and can be found in any of the standard FAQ repositories in the three-part form it is posted in.

Permission is granted to copy, archive, or otherwise make this FAQ available in any way you please, with only the following restriction: that in every place where this FAQ may be accessed, it must also be reasonably easy for a user to access a copy of the FAQ with its PGP signature(s) from me intact. This ensures that uncorrupted copies of the FAQ get propagated where those who care can check them, and also preserves attributions, etc. If you HTMLize this document, you can tag the two links mentioned above if you want to avoid storing multiple copies of the FAQ.

Future plans for the FAQ:
\begin{itemize}
\item Mac section!
\item hypertexting it and making it available in various forms (LaTeX, HTML, texinfo, or some such)
\end{itemize}

Any corrections or suggestions should be sent to me.

Jeff Licquia
\href{mailto:jalicqui@prairienet.org}{jalicqui@prairienet.org}


\end{document}